### 2020-04-20 draft_ABP.tex
update

\section{Configuration spaces with perfect $u$-equations from degenerating $A_n$ and $B_n$}
In this section we shall consider some degenerations of $A_n$ and $B_n$ and show that these form an infinite class of examples of binary geometries with perfect $u$-equations. To do this we shall use the fact that both $A_n$ and $B_n$ are generalised permutahedra and can be realised as a Minkowski sum of coordinate simplices.

@@

Let's define $[i,j]=\{i,i+1,\dots,j\}$ for $i,j\in \mathbb Z/(n+1)\mathbb Z$.
%For the symbol $X=x,u,S,F$, we also use the notation $X_{ij}:=X_{[i,j-1]}$.

The building set of $A_n$ is $\{[i,j]\,:\, 0\leq i\leq j\leq n\}$.
The facets are given by eq.\eqref{GPfacet}
\[
F^A_{[i,j]}=\sum_{i\leq k\leq l\leq j}S_{[k,l]},
\]
and their solution is 
\[
S_{[i,j]}=F^A_{[i,j]}+F^A_{[i+1,j-1]}-F^A_{[i,j-1]}-F^A_{[i+1,j]},
\]
where $F^A_{[k,l]}:=0$ when $k>l$ or $[k,l]=[0,n]$. Using this solution to rewrite the integrand
\[
\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{S_{[i,j]}}
=\prod_{0\leq i\leq j\leq n}\frac{x_{[i,j]}^{F^A_{[i,j]}}x_{[i,j]}^{F^A_{[i+1,j-1]}}}{x_{[i,j]}^{F^A_{[i,j-1]}}x_{[i,j]}^{F^A_{[i+1,j]}}}
=
\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F^A_{[i,j]}}
\prod_{1\leq i\leq j\leq n-1}x_{[i-1,j+1]}^{F^A_{[i,j]}}
\prod_{0\leq i\leq j\leq n-1}x_{[i,j+1]}^{-F^A_{[i,j]}}
\prod_{1\leq i\leq j\leq n}x_{[i-1,j]}^{-F^A_{[i,j]}},
\]
and we get that
\[
u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}} \quad \text{for $0\leq i\leq j\leq n$,}
\]
where $x_{[i,n+1]}:=1$ and  $x_{[-1,j]}:=1$. $u$-equations are
\[
1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl}.
\]

The building set of $B_n$ is $\{[i,i+k]\,:\,0\leq i, k\leq n\}$.
The facets are given by eq.\eqref{GPfacet}
\[
F^B_{[i,j]}=\sum_{[k,l]\subset [i,j]}S_{[k,l]},
\]
and their solution is 
\[
S_{[i,i]}=F^B_{[i,i]},\quad S_{[i,j]}=F^B_{[i,j]}+F^B_{[i+1,j-1]}-F^B_{[i,j-1]}-F^B_{[i+1,j]}\quad \text{for $i\neq j$},
\]
where $F^B_{[i+1,i]}:=0$. Therefore, the $u$-variables are
\[
u_i:=u_{[i,i-2]}=\frac{x_{[i,i-2]}}{x_{[0,n]}},\quad 
u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}}
\quad \text{for $i-j\neq 2$}.
\]
$u$-equations are
\[
1-u_i=U_{[i+1,i-1]},\quad 
1-u_{ij}=U_{[i+1,j],[j+1,i-1]}U_{[j+1,i-1],[i,j-1]}U^2_{[j+1,i-1]},
\]
where 
\[
U_{A,B}=\prod_{a\in A,b\in B}u_{ab},\quad 
U_A=\prod_{a\in A}u_a\prod_{a<b\in A}u_{ab}.
\]

$B_n$ type cluster stringy integral also comes from a hyperplane arrangement, the Shi arrangement.
The Shi arrangement contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
on the real line with the freedom of global transformation 
$z_i\to z_i+a$ which can be used to fix $z_{n+1}=0$. The Shi arrangement is 
given by the following hyperplanes
\[
	z_i-z_j=0\quad \text{and}\quad z_i-z_j=1\quad \text{for $1\leq i<j\leq n+1$},
\]
and its stringy integral is 
\[
\mathcal I_n = \int_{1>z_1>z_2>\cdots >z_n>0}
\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(1-z_1)(z_1-z_2)\cdots (z_{n}-0)}
\prod_{0\leq i<j \leq n}(z_i-z_j)^{s_{ij}}(1-z_i+z_j)^{t_{ij}},
\]
where the positive region is given by $0<z_i-z_j<1$ for $1\leq i<j \leq n+1$.
The $u$-variables of this configuration space are
\[
    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
\]
and 
\[
\begin{aligned}
    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
\end{aligned}
\]
where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices live in $\mathbb Z_{2n+2}$.
%They satisfy the following $u$-equations 
%\begin{align*}	
%1-u_{ij}&=\prod\limits_{j\prec k \prec i}u_k^2 u_{ki}u_{jk}\!\!\prod\limits_{j\prec k\prec l\prec i}u_{kl}^2\!\!\prod\limits_{\substack{j\prec k\prec i\\i\prec l\prec j}}u_{kl}u_{lk},\\
%1-u_{i}&=\prod\limits_{j\neq i}u_j \prod_{i\prec j\prec k\prec i}u_{jk},
%\end{align*}
%where labels are vertices of a $n$-gon and $\prec$ is the counterclockwise order on
%the $n$-gon.

@@

From the following equations for facets $\{F_{ij}\}$ of $A_n$
\[
F_{ac}+F_{bd}-F_{bc}-F_{ad}=\sum_{a\leq p<b\atop{c\leq q<d}}c_{pq}
\]
for $1\leq a<b<c<d\leq n+3$, an economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
\begin{align*}
    &F_{ac}+F_{bd}-F_{ad}=\sum_{a\leq p<b< q<d}c_{pq}\quad \text{for $a<b<c=b+1<d$ }\\
    \text{or}&\\
    &F_{1c}+F_{b,n+3}-F_{bc}=\sum_{1\leq p<b\atop{c\leq q<n+3}}c_{pq}\quad \text{for $a=1$ and $d=n+3$}
\end{align*}
to be zero, and all wanted degenerations can be got by setting $c$s in several above equations.

From the viewpoint of mesh, an equation above corresponds to a big diamond whose top or bottom corner and all $c$s are zero. For example,
\begin{center}
	\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
		\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$0$}
		-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$B$}-- cycle;
		\draw (-1,-1) -- (1,1);
		\draw (-1,1) -- (2,-2);
		\draw (0,-2) -- (2,0);
			\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,2) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,0) {};
	\end{tikzpicture}
	\qquad \text{or}
	\qquad
	\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
		\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$B$}
		-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$0$}-- cycle;
		\draw (-1,-1) -- (1,1);
		\draw (-1,1) -- (2,-2);
		\draw (0,-2) -- (2,0);
			\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-3) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,-1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,-2) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,-2) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
	\end{tikzpicture}
\end{center}
we can see that
\[
A+C-B=0.
\]
Since $A,B,C\geq 0$, the above equation forces $A$ and $C$ to vanish when $B=0$. Therefore, $B$ is no longer a facet of the degeneration. Similarly, black points are all vanishing facets in the above example, and generally
the number of vanishing facets equals the number of deleted $c$s for degenerations of this type.

One can use these diamonds to build a degeneration with more vanishing facets whose big polytope is a simplex. For example, in $A_3$
\begin{center}
\begin{tikzpicture}
	\fill[green!30] (2,1) -- (0,-1) -- (1,-2) -- (3,0);
	\fill[blue!30] (3,0) -- (2,-1) -- (3,-2) -- (4,-1);
	\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) -- (0,1);
	\draw[thick] (-1,-2) -- (2,1);
	\draw[thick] (-2,-1) -- (-1,-2);
	\draw[thick] (-1,0) -- (1,-2) -- (3,0);
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,0) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (3,0) {};
	\node at (-2.5,-1) {$13$};
\node at (-0.5,-1) {$24$};
\node at (1.5,-1) {$35$};
\node at (3.5,-1) {$46$};
\node at (-1.5,0) {$14$};
\node at (0.5,0) {$25$};
\node at (2.5,0) {$36$};
\node at (-0.5,1) {$15$};
\node at (1.5,1) {$26$};
\node at (1,2.2) {$16$};
\end{tikzpicture}
\end{center}
after setting $c$s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
\[
\{16,15,26,14,36,13,46\}.
\]
One can further check that it's a cube or $A_1^3$.

We can play the game for any degenerations of $A_n$, count black points and deleted $c$s in each degeneration, and find that for $A_2$, $A_3$ and $A_4$, there're respectively $5$, $42$ and $565$ possible degenerations whose big polytopes are simplices. For these degenerations, we can easily find their $u$-variables if their sets of all vanishing facets are known.

@@

The simplest degenerations of $A_n$ are those with one $c_{i,i+2}$ vanishing. For the one with $c_{i,i+2}=0$, we get 
\[
F_{i,i+3}=F_{i,i+2}+F_{i+1,i+3},
\]
so 
\[
\tilde u_{i,i+2}=u_{i,i+2} u_{i,i+3},\quad 
\tilde u_{i+1,i+3}=u_{i+1,i+3} u_{i,i+3},\quad 
\tilde u_I=u_I \text{ for the other $I\neq (i,i+3)$}.
\]
They satisfy the following $u$-equation
\[
1-\tilde u_{i,i+2}=\prod_{j\neq i,i+2,i+3} \tilde u_{i+1,j},\quad 
1-\tilde u_{i+1,i+3}=\prod_{j\neq i,i+2,i+3} \tilde u_{i+2,j}
\]
and $u$-equations for $\{u_{kl}\,:\, (k,l)\neq (i,i+3),(i,i+2),(i+1,i+3)\}$ with the change of variables above. Similarly, one can easily find the $u$-variables and $u$-equations for the degenerations with $c_{i,i+2}=0$ for several $i$.

The next simplest degenerations of $A_n$ is setting $c_{i-1,i+1}=c_{i,i+2}=c_{i-1,i+2}=0$, we have seen an example in $A_3$ above.

% For example, in the above example of $A_3$,
% \[
% F_{123}=F_{1}+F_2+F_3, \quad F_{12}=F_1+F_2, \quad F_{23}=F_2+F_3,
% \]
% so the $u$-variables are
% \begin{align*}
% \tilde u_{1}&=u_1 u_{123} u_{12}=\frac{x_1}{x_{01}},\quad 
% \tilde u_{2}=u_2 u_{123} u_{12}u_{23}=\frac{x_{2}}{x_{012}},\quad 
% \tilde u_{3}=u_3u_{123}u_{23}=\frac{x_3}{x_{0123}},\\
% \tilde u_{0}&=u_{0}=\frac{x_{0}}{x_{01}},\quad 
% \tilde u_{01}=u_{01}=\frac{x_{01}}{x_{012}},\quad 
% \tilde u_{012}=u_{012}=\frac{x_{012}}{x_{0123}},
% \end{align*}
% and they satisfy the following $u$-equations:
% \[
% 	\tilde u_1+\tilde u_0=1,\quad \tilde u_2+\tilde u_{01}=1,
% 	\quad \tilde u_{3}+\tilde u_{012}=1.
% \]

(Find those with perfect $u$-eq?)

*******************
\subsection*{Degenerations which lead to products}
In this section we provide an answer to the question of which degenerations of $A_n$ and $B_n$ give the most general products of such geometries. We begin by stating the following results about Nestohedra.

>>>>

\section{Configuration spaces with perfect $u$-equations from degenerating $A_n$ and $B_n$}
In this section we shall consider some degenerations of $A_n$ and $B_n$ and show that these form an infinite class of examples of binary geometries with perfect $u$-equations. To do this we shall use the fact that both $A_n$ and $B_n$ are generalised permutahedra and can be realised as a Minkowski sum of coordinate simplices. 
For future convenience, let's define $[i,j]=\{i,i+1,\dots,j\}$ for 
$i,j\in \mathbb Z/(n+1)\mathbb Z$.

@@

\subsubsection*{$n$-dimensional associahedron $\mathscr A_n$}

The building set of $\mathscr A_n$ is $\mathbf B= \{[i,j]\,:\, 0\leq i\leq j\leq n\}$.
The stringy canonical form of this building set $\mathcal I_{\mathbf B}(\{S\})$
is related with the original string integral eq.\eqref{stringint} by 
\[
	z_{j}-z_i=x_{[i,j-1]},
\]
so Mandelstam variables are related to $S$ by $s_{ij}=S_{[i,j-1]}$.
The facets of $\mathscr A_n$ are given by
\[
	F_{[i,j]}=\sum_{[k,l]\subset [i,j]}S_{[k,l]},
\]
and their solution is 
\begin{equation}\label{Ansf}
S_{[i,j]}=F_{[i,j]}+F_{[i+1,j-1]}-F_{[i,j-1]}-F_{[i+1,j]},
\end{equation}
where $F_{[k,l]}:=0$ when $k>l$ or $[k,l]=[0,n]$. Using this solution to rewrite 
the integrand of the stringy canonical form $\mathcal I_{\mathbf B}(\{S\})$
\begin{align*}
\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{S_{[i,j]}}
&=\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F_{[i,j]}}x_{[i,j]}^{F_{[i+1,j-1]}}\bigg /
x_{[i,j]}^{F_{[i,j-1]}}x_{[i,j]}^{F_{[i+1,j]}}\\
&=
\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F_{[i,j]}}
\prod_{1\leq i\leq j\leq n-1}x_{[i-1,j+1]}^{F_{[i,j]}}
\prod_{0\leq i\leq j\leq n-1}x_{[i,j+1]}^{-F_{[i,j]}}
\prod_{1\leq i\leq j\leq n}x_{[i-1,j]}^{-F_{[i,j]}},
\end{align*}
and we get that
\[
u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}} \quad \text{for $0\leq i\leq j\leq n$,}
\]
with $x_{[i,n+1]}:=1$ and $x_{[-1,j]}:=1$, whose $u$-equations are
\[
1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl}.
\]

The ABHY construction of $\mathscr A_n$ is given by 
\[
	S_{[i,j]}=-c_{[i,j]} \,\,\text{ for all $i<j$,}\quad
	F_{[i,j]}\geq 0 \,\,\text{ for all $i\leq j$},
\]
where $c$s are positive numbers. We can use a mesh to represent these conditions.
For example, the mesh of $\mathscr A_3$ is 
\begin{center}
\begin{tikzpicture}
	\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) node[below]{0} -- (0,1);
	\draw[thick] (-1,-2) node[below]{0} -- (2,1);
	\draw[thick] (-2,-1) -- (-1,-2);
	\draw[thick] (-1,0) -- (1,-2) node[below]{0}-- (3,0);
	\node at (-2.5,-1) {$[0,0]$};
	\node at (-0.65,-1) {$[1,1]$};
	\node at (1.35,-1) {$[2,2]$};
	\node at (3.35,-1) {$[3,3]$};
	\node at (-1.5,0) {$[0,1]$};
	\node at (0.35,0) {$[1,2]$};
	\node at (2.35,0) {$[2,3]$};
	\node at (-0.5,1) {$[0,2]$};
	\node at (1.35,1) {$[1,3]$};
	\node at (1,2.2) {$[0,3]$};
\end{tikzpicture}
\end{center}
Each diamond in the mesh whose top corner\footnote{
It looks different with the usual mesh where label of $c$ follows the left corner
in each diamond. This is because the mismatch of the correspondence of labels 
$F_{ij}=F_{[i,j-2]}$ and $s_{ij}=S_{[i,j-1]}$.
}
is label by $[i,j]$ represents 
\[
	c_{[i,j]}=F_{[i,j-l]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]},
\]
and each big diamond (which is made of several diamonds) gives us an equation
\[
	\sum_{i\leq a<j\atop{k<b\leq l}} c_{[a,b]} = 
	F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}
\]
where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$

\subsubsection*{$n$-dimensional cyclohedron $\mathscr B_n$}

The building set of $\mathscr B_n$ is $\mathbf B=\{[i,i+k]\,:\,0\leq i, k\leq n\}$.
The facets are given by 
\[
F_{[i,j]}=\sum_{[k,l]\subset [i,j]}S_{[k,l]},
\]
and their solution is 
\[
S_{[i,i]}=F_{[i,i]},\quad S_{[i,j]}=F_{[i,j]}+F_{[i+1,j-1]}-F_{[i,j-1]}-F_{[i+1,j]}\quad \text{for $i\neq j$},
\]
where $F_{[i+1,i]}:=0$. Therefore, the $u$-variables are
\[
u_i:=u_{[i,i-2]}=\frac{x_{[i,i-2]}}{x_{[0,n]}},\quad 
u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}}
\quad \text{for $i-j\neq 2$}.
\]
$u$-equations are
\[
1-u_i=U_{[i+1,i-1]},\quad 
1-u_{ij}=U_{[i+1,j],[j+1,i-1]}U_{[j+1,i-1],[i,j-1]}U^2_{[j+1,i-1]},
\]
where 
\[
U_{A,B}=\prod_{a\in A,b\in B}u_{ab},\quad 
U_A=\prod_{a\in A}u_a\prod_{a<b\in A}u_{ab}.
\]

Like $A_n$, $B_n$ type cluster stringy canonical form also comes from a hyperplane 
arrangement, the Shi arrangement. The Shi arrangement contains $n+1$ punctures 
$\{z_i\}_{i=1,\dots,n+1}$ on the real line with the freedom of global transformation 
$z_i\to z_i+a$ which can be used to fix $z_{n+1}=0$. The Shi arrangement is 
given by the following hyperplanes
\[
	z_i-z_j=0\quad \text{and}\quad z_i-z_j=1\quad \text{for $1\leq i<j\leq n+1$},
\]
and its stringy integral is 
\[
\mathcal I_n = \int_{1>z_1>z_2>\cdots >z_n>0}
\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(1-z_1)(z_1-z_2)\cdots (z_{n}-0)}
\prod_{0\leq i<j \leq n}(z_i-z_j)^{s_{ij}}(1-z_i+z_j)^{t_{ij}},
\]
where the positive region is given by $0<z_i-z_j<1$ for $1\leq i<j \leq n+1$.
The $u$-variables of this configuration space are
\[
    u_1=\tilde z_1-z_2,\quad \dots,\quad u_{n}=\tilde z_{n}-z_{n+1},
    \quad u_{n+1}=z_{n+1}-z_1
\]
and 
\begin{align*}
    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad \text{for $i<j$},\\
    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad \text{for $i<j$},
\end{align*}
where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices live in $\mathbb Z_{2n+2}$.
%They satisfy the following $u$-equations 
%\begin{align*}	
%1-u_{ij}&=\prod\limits_{j\prec k \prec i}u_k^2 u_{ki}u_{jk}\!\!\prod\limits_{j\prec k\prec l\prec i}u_{kl}^2\!\!\prod\limits_{\substack{j\prec k\prec i\\i\prec l\prec j}}u_{kl}u_{lk},\\
%1-u_{i}&=\prod\limits_{j\neq i}u_j \prod_{i\prec j\prec k\prec i}u_{jk},
%\end{align*}
%where labels are vertices of a $n$-gon and $\prec$ is the counterclockwise order on
%the $n$-gon.

@@

From the following equations for facets $\{F_{[i,j]}\}$ of $A_n$
\[
	F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}=
	\sum_{i\leq a<j\atop{k<b\leq l}} c_{[a,b]} 
\]
where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$,
an economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
\begin{align*}
&F_{[i,j-1]}+F_{[j,l]}-F_{[i,l]}= \sum_{i\leq a<j\leq b\leq l} c_{[a,b]} 
\quad \text{for $i<j=k+1\leq l$ }\\[-1.5ex]
\text{or}&\\
&F_{[0,k]}+F_{[j,n]}-F_{[j,k]}= \sum_{0\leq a<j\atop{k<b\leq n}} c_{[a,b]} 
\quad \text{for $0<j\leq n$ and $0\leq k<n$}
\end{align*}
to be zero, and all wanted degenerations can be got by setting $c$s in several above equations.

From the viewpoint of mesh, an equation above corresponds to a big diamond whose top or bottom corner and all $c$s are zero. For example,
\begin{center}
\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$0$}
	-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$B$}-- cycle;
\draw (-1,-1) -- (1,1);
\draw (-1,1) -- (2,-2);
\draw (0,-2) -- (2,0);
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,2) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,0) {};
\end{tikzpicture}
\qquad \text{or}\qquad
\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$B$}
-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$0$}-- cycle;
\draw (-1,-1) -- (1,1);
\draw (-1,1) -- (2,-2);
\draw (0,-2) -- (2,0);
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-3) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,-1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,-2) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,-2) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
\end{tikzpicture}
\end{center}
we can see that
\[
A+C-B=0.
\]
Since $A,B,C\geq 0$, the above equation forces $A$ and $C$ to vanish when $B=0$. Therefore, $B$ is no longer a facet of the degeneration. Similarly, black points are all vanishing facets in the above example, and generally
the number of vanishing facets equals the number of deleted $c$s for degenerations of this type.

One can use these diamonds to build a degeneration with more vanishing facets whose big polytope is a simplex. For example, in $A_3$
\begin{center}
\begin{tikzpicture}
\fill[green!30] (2,1) -- (0,-1) -- (1,-2) -- (3,0);
\fill[blue!30] (3,0) -- (2,-1) -- (3,-2) -- (4,-1);
\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) -- (0,1);
\draw[thick] (-1,-2) -- (2,1);
\draw[thick] (-2,-1) -- (-1,-2);
\draw[thick] (-1,0) -- (1,-2) -- (3,0);
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,0) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (3,0) {};
\node at (-2.5,-1) {$[0,0]$};
\node at (-0.65,-1) {$[1,1]$};
\node at (1.35,-1) {$[2,2]$};
\node at (3.35,-1) {$[3,3]$};
\node at (-1.5,0) {$[0,1]$};
\node at (0.35,0) {$[1,2]$};
\node at (2.35,0) {$[2,3]$};
\node at (-0.5,1) {$[0,2]$};
\node at (1.35,1) {$[1,3]$};
\node at (1,2.2) {$[0,3]$};
\end{tikzpicture}
\end{center}
after setting $c$s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
\[
	\{[0,3],[0,2],[0,1],[0,0],[1,1],[2,2],[3,3]\}.
\]
One can further check that it's a cube (or $A_1^3$).

We can play the game for any degenerations of $A_n$, count black points and deleted $c$s in each degeneration, and find that for $A_2$, $A_3$ and $A_4$, there're respectively $4$, $41$ and $580$ possible degenerations whose big polytopes are simplices. For these degenerations, we can easily find their $u$-variables if their sets of all vanishing facets are known.

@@

The simplest degenerations of $A_n$ are those with one $c_{[i,i+1]}$ vanishing. For the one with $c_{[i,i+1]}=0$, we get 
\[
	F_{[i,i+1]}=F_{i}+F_{i+1},
\]
where $F_i=F_{[i,i]}$, so 
\[
	\tilde u_{i}=u_{i} u_{[i,i+1]},\quad 
	\tilde u_{i+1}=u_{i+1} u_{[i,i+1]},\quad 
	\tilde u_I=u_I \text{ for the other $I\neq [i,i+1]$}.
\]
They satisfy the following $u$-equation
\[
	1-\tilde u_{i}=\prod_{0\leq a\leq i-1}\tilde u_{[a,i-1]}
	\prod_{i+1< b\leq n} \tilde u_{[i+1,b]},\quad 
	1-\tilde u_{i+1}=\prod_{0\leq a <i-1} \tilde u_{[a,i]}
	\prod_{i+2\leq b\leq n} \tilde u_{[i+2,b]},\quad 
\]
and the other $u$-equations are original $u$-equations for
$\{u_{[i,j]}\,:\, [i,j]\neq [i,i],[i,i+1],[i+1,i+1]\}$ in terms of new variables. Similarly, one can easily find the $u$-variables and $u$-equations for the degenerations with $c_{[i,i+1]}=0$ for several $i$.

%The next simplest degenerations of $A_n$ is setting $c_{[i-1,i]}=c_{[i,i+1]}=c_{[i-1,i+1]}=0$ for $1\leq i\leq n-1$, we have seen an example in $A_3$ above. The vanishing facets of this degeneration are
%\[
	%F_{[i-1,i+1]}=F_{i-1}+F_i+F_{i+1},\quad F_{[i-1,i]}=F_{i-1}+F_i,
	%\quad F_{[i,i+1]}=F_i+F_{i+1},
%\]
%so $u$-variables of this degeneration are 
%\[
	%\tilde u_{i-1}=u_{i-1}u_{[i-1,i+1]}u_{[i-1,i]}, \quad 
	%\tilde u_{i}=u_iu_{[i-1,i+1]}u_{[i,i+1]},\quad
	%\tilde u_{i+1}=u_{i+1}u_{[i-1,i+1]}u_{[i,i+1]} 
%\]
%and $\tilde u_I=u_I$ for the other $I$. ($u$-eqs...)

The nest simplest degenerations of $\mathscr A_n$ may be products 
$\mathscr A_i\times \mathscr A_{n-i}$, which can be realized as the following
mesh,
\begin{center}
\usetikzlibrary{decorations.pathmorphing}
\begin{tikzpicture}[scale=2]
\fill[green!20] (0.4498,-0.558) -- (1.2997,-1.4584) -- (2.8779,0.1223) --(2,1);
\draw (-0.5,-1.5) -- (2,1) -- (4.5,-1.5);
\draw[decorate,decoration=zigzag] (-0.5,-1.5)--(4.5,-1.5);
\node at (1.7,-1.3) {$[i,i]$};
\node at (0.3,-0.4) {$[0,i]$};
\node at (3.1,0.2) {$[i,n]$};
\end{tikzpicture}
\end{center}
where $c$s in green region vanish, \emph{i.e.} $c_{[a,b]}=0$ for $0\leq a<i<b\leq n$.
Vanishing facets of this degeneration are
\[
F_{[a,b]}=F_{[a,n]}+F_{[0,b]}\quad \text{for $0<a\leq i\leq b<n$},
\]
so new $u$-variables are
\[
	\tilde u_{[0,b]} = u_{[0,b]}\prod_{a=1}^{i} u_{[a,b]},\quad 
	\tilde u_{[a,n]} = u_{[a,n]}\prod_{b=i}^{n-1} u_{[a,b]},
\]
and $\tilde u_{I}=u_{I}$ for the other $I$. The $u$-equations are the union of 
$u$-equations of the following two independent meshes
\begin{center}\footnotesize
\begin{tikzpicture}[scale=1.5,baseline={([yshift=-.5ex]current bounding box.center)}]
\draw (0.5,-2.5) -- (3,0) -- (5.5,-2.5);
\draw (5.5,-2.5) -- (5,-3) -- (2.5,-0.5);
\draw (5,-2) -- (4,-3) -- (2,-1);
\draw (4.5,-1.5) -- (3,-3) -- (1.5,-1.5);
\draw (0.5,-2.5) -- (1,-3) -- (3.5,-0.5);
\node at (2,-2.8) {$\cdots$};
\node at (2.6,-2.1) {$\ddots$};
\node at (3.1,-1.6) {$\ddots$};
\node at (3.6,-1.1) {$\ddots$};
\node at (0.3,-2.5) {$[0,0]$};
\node at (3.1,-2.5) {$[i{-}2,i{-}2]$};
\node at (4.1,-2.5) {$[i{-}1,i{-}1]$};
\node at (5.2,-2.5) {$[i,n]$};
\node at (4.6,-2) {$[i{-}1,n]$};
\node at (3.6,-2) {$[i {-}2,i{-}1]$};
\node at (4.2,-1.5) {$[i{-}2,n]$};
\node at (3.2,-0.5) {$[1,n]$};
\node at (3,0.2) {$[0,n]$};
\node at (2.1,-0.5) {$[0,i{-}1]$};
\node at (1.7,-1) {$[0,i{-}2]$};
\end{tikzpicture}\quad 
\begin{tikzpicture}[scale=1.5,baseline={([yshift=-.5ex]current bounding box.center)}]
\draw (0.5,-2.5) -- (3,0) -- (5.5,-2.5);
\draw (5.5,-2.5) -- (5,-3) -- (2.5,-0.5);
\draw (4.5,-1.5) -- (3,-3) -- (1.5,-1.5);
\draw (4,-1) -- (2,-3) -- (1,-2);
\draw (0.5,-2.5) -- (1,-3) -- (3.5,-0.5);
\node at (4,-2.6) {$\cdots$};
\node[rotate=90] at (3.2,-2.2) {$\ddots$};
\node[rotate=90] at (2.7,-1.7) {$\ddots$};
\node[rotate=90] at (2.2,-1.2) {$\ddots$};
\node at (3,0.2) {$[0,n]$};

\node at (3.9,-0.5) {$[i{+}1,n]$};
\node at (4.4,-1) {$[i{+}2,n]$};
\node at (4.9,-1.5) {$[i{+}3,n]$};
\node at (2.1,-0.5) {$[0,n{-}1]$};
\node at (1.2,-1.4) {$[0,i{+}2]$};
\node at (0.2,-2.5) {$[0,i]$};
\node at (0.6,-2) {$[0,i{+}1]$};
\node at (1.2,-2.5) {$[i{+}1,i{+}1]$};
\node at (1.7,-2) {$[i{+}1,i{+}2]$};
\node at (2.1,-2.5) {$[i{+}2,i{+}2]$};
\end{tikzpicture}
\end{center}
